Determinism, Complexity, and Predictability in Computer Performance

### 2014-01-27 pecomplexity.tex
add new figures

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1.0\textwidth]{figs/prediction_vs_entropy}
  \caption{The improvement of LMA over na\"{i}ve vs weighted permutation entropy.
  For each of these, the word length used is $5$.}
  \label{fig:pred_vs_ent}
\end{figure}

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1.0\textwidth]{figs/LMA_prediction_vs_entropy}
  \caption{The MASE of LMA vs weighted permutation entropy. For each of these,
  the word length used is $5$.}
  \label{fig:lma_pred_vs_ent}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1.0\textwidth]{figs/ARIMA_prediction_vs_entropy}
  \caption{The MASE of ARIMA vs weighted permutation entropy. For each of these,
  the word length used is $5$.}
  \label{fig:arima_pred_vs_ent}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1.0\textwidth]{figs/prediction_vs_entropy}
  \caption{The best MASE among all runs and prediction methods vs weighted
  permutation entropy. For each of these, the word length used is $5$.}
  \label{fig:pred_vs_ent}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1.0\textwidth]{figs/LMA_vs_ARIMA}
  \caption{The MASE values for LMA against ARIMA. The dashed line is the
  identity.}
  \label{fig:lma_vs_arima}
\end{figure}
